\begin{fullwidth} 
    \subsection{Summarize the techniques used in security assessments}
    \subsubsection*{\color{red}Threat Hunting}
    \begin{itemize}
        \item \textbf{Intelligence Fusion:} Combining various sources of information to generate actionable intelligence about threats.
        \item \textbf{Threat Feeds:} Streams of data related to potential threats, like IP addresses known to be malicious.
        \item \textbf{Advisories and Bulletins:} Alerts and notifications regarding new threats or vulnerabilities.
        \item \textbf{Maneuver:} Adapting to or moving against a threat to neutralize it.
    \end{itemize}
    \subsubsection*{\color{red}Vulnerability Scans}
    \begin{itemize}
        \item \textbf{False Positives:} Alerts on vulnerabilities that aren’t actually present (false alarms).
        \item \textbf{False Negatives:} Failing to detect an actual vulnerability (missing a real threat).
        \item \textbf{Log Reviews:} Analyzing logs to identify suspicious activity.
        \item \textbf{Credentialed vs. Non-credentialed:} Scans with login credentials vs. those without to see system vulnerabilities from different viewpoints.
        \item \textbf{Intrusive vs. Non-intrusive:} Scans that might impact system performance vs. those that don’t.
        \item \textbf{Application/Web Application/Network:} Scans targeting different elements: software applications, web platforms, or network infrastructure.
        \item \textbf{CVE/CVSS:} Standardized identifiers and scorings for vulnerabilities.
        \item \textbf{Configuration Review:} Checking system setups for vulnerabilities.
    \end{itemize}

    \subsubsection*{\color{red}Syslog/Security Information and Event Management (SIEM)}
    \begin{itemize}
        \item \textbf{Review Reports:} Analyzing compiled data and insights.
        \item \textbf{Packet Capture:} Collecting data packets transmitted over networks for analysis.
        \item \textbf{Data Inputs:} Different types of data fed into the SIEM for analysis.
        \item \textbf{User Behavior Analysis:} Studying how users interact with systems to identify anomalies.
        \item \textbf{Sentiment Analysis:} Utilizing data analysis to understand sentiments or attitudes expressed in source data.
        \item \textbf{Security Monitoring}: Continuously observing systems to detect and respond to security incidents.
        \item \textbf{Log Aggregation:} Collecting log data from different sources into a single location.
        \item \textbf{Log Collectors:} Systems or applications that gather log data.
    \end{itemize}

    \subsubsection*{\color{red}Security Orchestration, Automation, and Response (SOAR)}
    \begin{itemize}
        \item \textbf{Security Orchestration:} Coordinating and structuring how different security solutions work together.
        \item \textbf{Automation:} Utilizing technology to perform tasks without human intervention.
        \item \textbf{Response:} Actions taken to mitigate, prevent, or remediate security incidents.
    \end{itemize}

\end{fullwidth}
\newpage